Brief Announcement: An Improved Lower Bound for Dynamic Balanced Graph Partitioning

### 2020-02-16 paper/paper.tex
Styling PPL
ACM keywords done

\keywords{online algorithms, competitive analysis}

@@

%      \maciek{``re-partition'' procedure name should indicate the fact that this is a specific repartition that is close to initial partition}
      We note that the $\mathit{re\mhyphen partition}$ at Line \ref{line:rebalance} replaces the current configuration $P$ with a perfect partition closest to $P_I$.
Hence it never moves to a configuration beyond distance $\Delta$.      
\begin{property} \label{prop:dist<OPT}
    Let $P$ be any configuration chosen by Algorithm \ref{alg:ppl} at Line $\ref{line:rebalance}$.
    Then, $\dist(P,P_I) \leq \Delta$.
\end{property}

@@

\todo{ACM keywords are mandatory}

>>>>

\keywords{online algorithms, competitive analysis, graph partitioning, clustering}

@@

%      \maciek{``re-partition'' procedure name should indicate the fact that this is a specific repartition that is close to initial partition}
      We note that the $\mathit{re\mhyphen partition}$ at Line \ref{line:rebalance} replaces the current configuration $P$ with a perfect partition closest to $P_I$.
Hence it never moves to a configuration beyond distance $\Delta$.      
\begin{property} \label{prop:dist<OPT}
    Let $P$ be any configuration chosen by \PPL at Line $\ref{line:rebalance}$.
    Then, $\dist(P,P_I) \leq \Delta$.
\end{property}

@@
